\ieeetitle

### 2016-12-23 report/introduction.tex
Continue work on thesis

Until now, the creators of \epto have only tested this algorithm in a simulated environment. In this work, we implement \epto in pure Kotlin and introduce a benchmarking solution to show that \epto is suitable for real-world large-scale distributed systems. We compare \epto to the deterministic total order algorithm provided by \jgroups \autocite{jgroups} in both stable and unstable environments. \epto uses a PSS CYCLON to obtain a random view, coupled with a tracker that keeps track of dead and alive peers to obtain a first initial view. These benchmarks can easily be launched and scaled on a cluster using Docker and Docker Swarm. Furthermore, we can inject synthetic or real churn\footnote{Using the Failure Trace Archive databases} in the system.

@@

The next sections are dedicated to present our benchmarking solution and to present the results obtained. Section \ref{sec:ordering} presents the different kind of ordering. Section \ref{sec:epto} presents \epto and the architecture of our implementation. Section \ref{sec:evaluation} shows and explains the results obtained. We then argue about future work in section \ref{sec:future-work}. We finally draw conclusions in section \ref{sec:conclusion}.

>>>>

Until now, the creators of \epto have only tested this algorithm in a simulated environment. In this work, we implement \epto in pure Kotlin and introduce a benchmarking solution to show that \epto is suitable for real-world large-scale distributed systems. We compare \epto to the deterministic total order algorithm provided by \jgroups \autocite{jgroups} in both stable and unstable environments. \epto uses a PSS CYCLON \autocite{Voulgaris2005} to obtain a random view, coupled with a tracker that keeps track of dead and alive peers to obtain a first initial view. These benchmarks can easily be launched and scaled on a cluster using Docker and Docker Swarm. Furthermore, we can inject synthetic or real churn\footnote{Using the Failure Trace Archive databases} in the system.

@@

The next sections are dedicated to present our benchmarking solution and to present the results obtained. Section \ref{sec:ordering} presents the different kind of ordering. Section \ref{sec:definitions} defines the terms used in the paer. Section \ref{sec:epto} presents \epto and the architecture of our implementation. Section \ref{sec:evaluation} shows and explains the results obtained. We then argue about future work in section \ref{sec:future-work}. We finally draw conclusions in section \ref{sec:conclusion}.
